A new tidy data structure to support exploration and modeling of temporal data

### 2019-08-29 tsibble.Rmd
section 4.2-3

Modeling is crucial to explanatory and predictive analytics, where time series and longitudinal data analysis start to diverge. Nevertheless, tsibble as a model-oriented object can flow into both types of models, with new semantics (index and key) to be internally utilized, to accelerate modelling.

Most time series models are univariate, such as ARIMA and Exponential Smoothing, modelling temporal dynamics for each series independently. The **fable** package [@R-fable] provides a tidy forecasting framework built on top of tsibble, which is under development, with the goal of promoting transparent and human-centered forecasting practices. With the presence of the key, tsibble holds many series. Since models are fundamentally scalable, the `model()` and `forecast()` generics will take care of fitting and forecasting univariate models to each series across time in a tsibble at once.

Panel data models, however, put emphases on overall, within, and between variations both across individuals and time. Fixed and random effects models can be developed in line with the **fable** design.

>>>>

Modeling is crucial to explanatory and predictive analytics, where time series and longitudinal data analysis diverges. The tsibble, as a model-oriented object, can flow into both types of modelling, and the new semantics (index and key) can be internally utilized to accelerate modelling.

Most time series models are univariate, such as ARIMA and Exponential Smoothing, modelling temporal dynamics for each series independently. The **fable** package [@R-fable], currently under development, provides a tidy forecasting framework built on top of tsibble, with the goal of promoting transparent and human-centered forecasting practices. With the presence of the key, a tsibble can hold many series. Since models are fundamentally scalable, the `model()` and `forecast()` generics will take care of fitting and forecasting univariate models to each series across time in a tsibble at once.

Panel data models, however, put emphases on overall, within, and between variation both across individuals and time. Fixed and random effects models could be developed in line with the **fable** design.
